\textbf{CMCS 818J Project Final Report}

### 2012-12-18 doc/final_report/draft_report.tex

>>>>

	The estimated memory footprint of the public key matrices grows rapidly with an increasing security parameter, but slowly with increasing stream size.
	The reason for this is that the scheme calls for matrices of size k x k log q.
	The matrix size grows faster than k SQUARED because q also depends on k.
	Fortunately, the current proposal is to pick a security parameter "large enough", say 500, and not to vary k over time.

	Future benchmarking efforts will also measure the memory footprint of the prover over time, and the size of a proof for varying parameter sizes.
	Additionally, we will benchmark the time required to perform the following tasks:

	\begin{itemize}
	\item Update prover state	
	\item Proof generation
	\item Update verifier state
	\item Proof verification
	\item Matrix multiplication using built-in Ruby implementation
	\item Matrix multiplication using optimized libraries
	\end{itemize}
